Supervised Learning for Psychological Attention to High School Students

### 2020-11-18 article/article.tex
[ article ] finished methodology

@@

Additionally, it is well-known that the bound for the training dataset size is
given by
\begin{equation}
  N\geq \dfrac{\ln(2)}{2\epsilon^2}\left[(2^k-1)(1+\log_2 m) + 1 + \ln\left(
  \dfrac{1}{\delta}\right)\right],
\end{equation}
but again, the size of the dataset is fixed. Thus, $\epsilon$ was calculated by
fixing the tree depth $k$ and setting $\delta=0.7$.............

@@

\section{Results for Embedded Data}
This section presents the same results above presented but for the data
embedded with the TSNE algorithm prior to training.
\subsection{Support Vector Machines}
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/svm-emb-linear-contour-0-1.pdf}
  \caption{Linear kernel SVM contour with real labels.}
\end{figure}

@@

\subsection{Decision Tree}
\begin{figure}
    \includegraphics[width=\columnwidth]{figs/tree-emb-graph.pdf}
    \caption{Decision tree.}
\end{figure}

@@

\begin{table}
\centering
\caption{Performance scores for DT.}
\label{tab:DT_emb}
\begin{tabular}{cll}
\hline
\textbf{Set} & \multicolumn{1}{c}{\textbf{Sensitivity}} & \multicolumn{1}{c}{\textbf{Specificity}} \\ \hline
Training & 1 & 1 \\
Testing & 0 & 1 \\
Validation & 0.63 & 0.94 \\ \hline
\end{tabular}
\end{table}

>>>>

Furthermore, it is important to notice that the dataset is 6-dimensional, which
clearly brings problems for visualizing the learning machines' outputs and
decision boundaries. In this paper, the decision functions of the fitted
learning machines will be presented using contour plots of the projected data.
This process will better described: each 6-dimensional pattern generates an
output whenever it is evaluated in the fitted model. The idea is to generate an
equally-spaced grid in $[-1,1]^6$ and evaluate each point on this model, in
order to plot the contour of the shattering function. The main issue is that a
direct projection into a 2-dimensional space of each point on the grid is not
necessarily a function, since several points can have the same projection, but
different values of the shattering function. In order to address this issue,
the mean of the points that mapped into the same projection is taken, giving an
proxy of the general behavior in high dimensions. This ``mean'' projection
contour plots also include the projection of the training data points into the
same coordinates and scattered with the real labels, giving an idea of the
classification performance in high dimensions. Remark: as stated, the survey
data also includes the outputs of the Fuzzy Inference System; thus, the countour
plots are presented only for relating first input with the first input, second
with the second output and so on. This was done aiming at two objectives:
keeping a reasonable number of plots in the document, and giving a more
intuitive interpretation to these plots.

@@

Additionally, it is well-known that the bound for the training dataset size is
given by
\begin{equation}
  N\geq \dfrac{\ln(2)}{2\epsilon^2}\left[(2^k-1)(1+\log_2 m) + 1 + \ln\left(
  \dfrac{1}{\delta}\right)\right],
\end{equation}
but again, the size of the dataset is fixed. Thus, $\epsilon$ was calculated by
fixing the tree depth $k=4$ and setting $\delta=0.7$ yielding a value of
$\epsilon=0.5381$, which is a suitable value for the classifier error.

@@

\section{Results for Embedded Data}
This section presents the same results above presented but for the data
embedded with the TSNE algorithm prior to training.

\subsection{Support Vector Machines}
The PAC learning, results using the same optimization-sensitivity methodology,
are presented in Fig. \ref{fig:error-SVM-emb}

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/svm-emb-linear-error.pdf}
        \caption{Linear SVM.}
    \end{subfigure}
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/svm-emb-poly-error.pdf}
        \caption{Polynomial SVM}
    \end{subfigure}
    \caption{Estimated $\epsilon$ for different training set sizes.}
    \label{fig:error-SVM-emb}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/svm-emb-linear-contour-0-1.pdf}
  \caption{Linear kernel SVM contour with real labels.}
\end{figure}

@@

\subsection{Decision Tree}
The estimated value of $\epsilon$ for the given training dataset size, taking
$m=2$, a tree depth $k=5$ and a fixed $\delta=0.3$ is 0.5763.
\begin{figure}
    \includegraphics[width=\columnwidth]{figs/tree-emb-graph.pdf}
    \caption{Decision tree.}
\end{figure}

@@

\begin{table}
\centering
\caption{Performance scores for DT.}
\label{tab:DT_emb}
\begin{tabular}{ccc}
\hline
\textbf{Set} & \textbf{Sensitivity} & \textbf{Specificity} \\ \hline
Training & 1 & 1 \\
Testing & 0 & 1 \\
Validation & 0.63 & 0.94 \\ \hline
\end{tabular}
\end{table}
